---
title: "ABN multilevel modelling brms - resp - fb"
author: "Davide Gheza"
date: "17 augustus 2018"
output: 
  html_document: 
    code_folding: hide
    toc: true
    theme: united
  pdf_document: default
encoding: UTF-8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load required packages:
```{r, cache=FALSE}

if (!require("brms")) install.packages("brms")
library(brms)
theme_set(theme_default())

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

if (!require("BEST")) install.packages("BEST")
library(BEST)
```

## Load data 
```{r}
rm(list=ls())   # clear all!
wd <- ("C:/Users/gdavide/Documents/MATLAB/dg_workspace/Final_reanalysis_2017/results/HC vs MDDT1 - 34 sbj/total induced evoked Theta 3-7 Hz/")
setwd(wd) # set work directory
ABN <- read.csv2("theta HC vs MDDT1 - 34 matched - FCz Fz - induced 3-7 Hz _ for R - CABN revision.csv",header=TRUE,na.strings="NaN") # read data

head(ABN)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Preparation of data 
```{r}

# filter out useless data

ABN = subset(ABN, select = c("T.resp.cor.50","T.resp.cor.80","T.resp.cor.100","T.resp.inc.50","T.resp.inc.80","T.resp.inc.100","T.fb.cor.50","T.fb.cor.80","T.fb.cor.100","T.fb.inc.50","T.fb.inc.80","T.fb.inc.100","group","sn"))

# long format
ABN = gather(ABN, key = "cond", value = "power", T.resp.cor.50:T.fb.inc.100)

# create factor level
ABN = ABN %>% mutate(level = rep(c("resp","fb"), each = (length(unique(ABN$power))/2)))   

# create factor accuracy
ABN$accuracy[(ABN$cond %in% c("T.resp.cor.50","T.resp.cor.80","T.resp.cor.100","T.fb.cor.50","T.fb.cor.80","T.fb.cor.100"))] = "cor"
ABN$accuracy[(ABN$cond %in% c("T.resp.inc.50","T.resp.inc.80","T.resp.inc.100","T.fb.inc.50","T.fb.inc.80","T.fb.inc.100"))] = "inc"

# create factor prob
ABN$prob[(ABN$cond %in% c("T.resp.cor.50","T.resp.inc.50","T.fb.cor.50","T.fb.inc.50"))] = "50"
ABN$prob[(ABN$cond %in% c("T.resp.cor.80","T.resp.inc.80","T.fb.cor.80","T.fb.inc.80"))] = "80"
ABN$prob[(ABN$cond %in% c("T.resp.cor.100","T.resp.inc.100","T.fb.cor.100","T.fb.inc.100"))] = "100"
                      

ABN = ABN %>% mutate(snG = paste0(ABN$group, ABN$sn))          # group-dependent coding for sbj

                  
ABN = ABN %>%
        mutate(snG = as.factor(ABN$snG))    %>%                   # snG variable as factor
        mutate(level = as.factor(ABN$level))    %>%               # level variable as factor
        mutate(accuracy = as.factor(ABN$accuracy))    %>%         # accuracy variable as factor
        mutate(prob = as.factor(ABN$prob))                        # prob variable as factor    
  


# prepare conditions for marginal effects

conditions <- make_conditions(ABN, c("accuracy", "prob", "group")) 
```

## define level: response - feedback
```{r}

ABN = ABN %>%  filter(level == "resp")
                 

```


### Analyse the data

## 1) fitting a compact model with accuracy

```{r, results="hide"}

fit_acc = readRDS(file = "ABN_fb_acc")

fit_acc <- brm(power ~ 1 + accuracy + (1 + accuracy | snG), data = ABN, cores = 8,
                   control = list(adapt_delta = 0.99))

# saveRDS(fit_acc,file = "ABN_fb_acc")
```
Summarize results:
```{r}
summary(fit_acc)
```

Plot fit:
```{r}
plot(fit_acc, ask = FALSE)
```
Visualize predictions:
```{r}
plot(marginal_effects(fit_acc), points = TRUE, ask = FALSE)
```
Check model fit:
```{r}
pp_check(fit_acc)
```

## 2) fitting a model with main effects of accuracy and probability

```{r, results="hide"}

fit_accprob = readRDS(file = "ABN_fb_accprob")

fit_accprob <- brm(power ~ 1 + accuracy + prob + (1 + accuracy + prob | snG), data = ABN, cores = 8,
                   control = list(adapt_delta = 0.99))

# saveRDS(fit_accprob,file = "ABN_fb_accprob")
```
Summarize results:
```{r}
summary(fit_accprob)
```
Plot fit:
```{r}
plot(fit_accprob, ask = FALSE)
```
Visualize predictions:
```{r}
plot(marginal_effects(fit_accprob), points = TRUE, ask = FALSE)

# prepare conditions for marginal effects
conditions <- make_conditions(ABN, c("accuracy", "prob")) 

me <- marginal_effects(fit_accprob, conditions = conditions, 
                        re_formula = NULL)
plot(me, ncol = 3, points = TRUE, ask = FALSE)
```
Check model fit:
```{r}
pp_check(fit_accprob)
```

## 3) fitting a model with main effects (accuracy,probability,group)

```{r, results="hide"}

fit_maineff = readRDS(file = "ABN_fb_maineff")

fit_maineff <- brm(power ~ 1 + accuracy + prob + group + (1 + accuracy + prob | snG), data = ABN, cores = 8,
                   control = list(adapt_delta = 0.99))

# saveRDS(fit_maineff,file = "ABN_fb_maineff")
```
Summarize results:
```{r}
summary(fit_maineff)
```
Plot fit:
```{r}
plot(fit_maineff, ask = FALSE)
```
Visualize predictions:
```{r}
plot(marginal_effects(fit_maineff), points = TRUE, ask = FALSE)

# prepare conditions for marginal effects
conditions <- make_conditions(ABN, c("accuracy", "prob", "group")) 

me2 <- marginal_effects(fit_maineff, conditions = conditions, 
                        re_formula = NULL)
plot(me2, ncol = 3, points = TRUE, ask = FALSE)
```
Check model fit:
```{r}
pp_check(fit_maineff)
```

## 4) fitting a model with main effects (accuracy,probability,group) and interaction prob : group

```{r, results="hide"}

fit_full = readRDS(file = "ABN_fb_full")

fit_full <- brm(power ~ 1 + accuracy + prob*group + (1 + accuracy + prob | snG), data = ABN, cores = 8,
                   control = list(adapt_delta = 0.99))

# saveRDS(fit_full,file = "ABN_fb_full")
```
Summarize results:
```{r}
summary(fit_full)
```
Plot fit:
```{r}
plot(fit_full, ask = FALSE)
```
Visualize predictions:
```{r}
plot(marginal_effects(fit_full), points = TRUE, ask = FALSE)

# prepare conditions for marginal effects
conditions <- make_conditions(ABN, c("accuracy", "prob", "group")) 

me2 <- marginal_effects(fit_full, conditions = conditions, 
                        re_formula = NULL)
plot(me2, ncol = 3, points = TRUE, ask = FALSE)
```
Check model fit:
```{r}
pp_check(fit_full)
```

# Compare all 4 models:
Leave one out + Watababe-Akaike information criteria
```{r}
loo(fit_full, fit_maineff, fit_accprob, fit_acc, reloo = TRUE, cores = 8)
WAIC(fit_full, fit_maineff, fit_accprob, fit_acc, cores = 8)
```

Compute model weights:
```{r}
model_weights(fit_full, fit_maineff, fit_accprob, fit_acc, weights = "waic")
```
Check explained variance:
```{r}
bayes_R2(fit_acc)
bayes_R2(fit_accprob)
bayes_R2(fit_maineff)
bayes_R2(fit_full)
```

### Model of interest: #4
## Build posterior distribution for each condition

```{r}

post <- posterior_samples(fit_full,"^b") # extracting posterior samples for fixed effects

HCcor100 = post[["b_Intercept"]]

HCcor80 = post[["b_Intercept"]] + post[["b_prob80"]]

HCcor50 = post[["b_Intercept"]] + post[["b_prob50"]]

HCinc100 = post[["b_Intercept"]] + post[["b_accuracyinc"]]

HCinc80 = post[["b_Intercept"]] + post[["b_accuracyinc"]] + post[["b_prob80"]]

HCinc50 = post[["b_Intercept"]] + post[["b_accuracyinc"]] + post[["b_prob50"]]

MDDcor100 = post[["b_Intercept"]] + post[["b_groupMDDT1"]]

MDDcor80 = post[["b_Intercept"]] + post[["b_groupMDDT1"]] + post[["b_prob80"]] + post[["b_prob80:groupMDDT1"]] 

MDDcor50 = post[["b_Intercept"]] + post[["b_groupMDDT1"]] + post[["b_prob50"]] + post[["b_prob50:groupMDDT1"]]

MDDinc100 = post[["b_Intercept"]] + post[["b_accuracyinc"]] + post[["b_groupMDDT1"]]
 
MDDinc80 = post[["b_Intercept"]] + post[["b_accuracyinc"]] + post[["b_groupMDDT1"]] + 
  post[["b_prob80"]] + post[["b_prob80:groupMDDT1"]]

MDDinc50 = post[["b_Intercept"]] + post[["b_accuracyinc"]] + post[["b_groupMDDT1"]] + 
  post[["b_prob50"]] + post[["b_prob50:groupMDDT1"]]


# compute mean of posterior posterior distributions to compare to raw data

full.post.power = c(mean(HCcor100), mean(HCcor80), mean(HCcor50), mean(HCinc100), mean(HCinc80), mean(HCinc50),
                         mean(MDDcor100), mean(MDDcor80), mean(MDDcor50), mean(MDDinc100), mean(MDDinc80), mean(MDDinc50))

full.post.label = c("HCcor100", "HCcor80", "HCcor50", "HCinc100", "HCinc80", "HCinc50", 
                         "MDDcor100", "MDDcor80", "MDDcor50", "MDDinc100", "MDDinc80", "MDDinc50")

full.post = data.frame(full.post.power,full.post.label)


# plot

## specify levels order
full.post$full.post.label = factor(full.post$full.post.label,
                   levels = c("HCcor100", "HCcor80", "HCcor50", "HCinc100", "HCinc80", "HCinc50", 
                              "MDDcor100", "MDDcor80", "MDDcor50", "MDDinc100", "MDDinc80", "MDDinc50"),
                   labels = c("HCcor100", "HCcor80", "HCcor50", "HCinc100", "HCinc80", "HCinc50", 
                              "MDDcor100", "MDDcor80", "MDDcor50", "MDDinc100", "MDDinc80", "MDDinc50"))

full.post %>%
  ggplot(aes(x = full.post.label, y = full.post.power)) +
  stat_summary(fun.y=mean, geom="point", shape=4, size=5, color="black") +
  theme(axis.text = element_text(size = 7),
        axis.title = element_text(size = 16))


```

## Test some hypotheses

# --> the group difference of the prob difference is equal for correct or incorrect (since we did not model the acc interaction)
```{r}
### 100 - 50

## incorrect trials: prob 100 - 50 is larger in HC vs MDD

# Difference between high and low probability, in each group - incorrect trials
HC_diff_inc_100_50 = HCinc100 - HCinc50
MDD_diff_inc_100_50 = MDDinc100 - MDDinc50

# Group difference of the prob difference
group_difference_inc_100_50 = HC_diff_inc_100_50 - MDD_diff_inc_100_50


# plot posterior probability distribution (on the above contrasts)
## HC inc prob 100 - 50
plotPost(HC_diff_inc_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## MDD inc prob 100 - 50
plotPost(MDD_diff_inc_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## difference of the difference
plotPost(group_difference_inc_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)


## correct trials: prob 100 - 50 is larger in HC vs MDD

# Difference between high and low probability, in each group - correct trials
HC_diff_cor_100_50 = HCcor100 - HCcor50
MDD_diff_cor_100_50 = MDDcor100 - MDDcor50

# Group difference of the prob difference
group_difference_cor_100_50 = HC_diff_cor_100_50 - MDD_diff_cor_100_50


# plot posterior probability distribution (on the above contrasts)
## HC inc prob 100 - 50
plotPost(HC_diff_cor_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## MDD inc prob 100 - 50
plotPost(MDD_diff_cor_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## difference of the difference
plotPost(group_difference_cor_100_50, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)




### 100 - 80

## incorrect trials: prob 100 - 80 is larger in HC vs MDD

# Difference between high and low probability, in each group - incorrect trials
HC_diff_inc_100_80 = HCinc100 - HCinc80
MDD_diff_inc_100_80 = MDDinc100 - MDDinc80

# Group difference of the prob difference
group_difference_inc_100_80 = HC_diff_inc_100_80 - MDD_diff_inc_100_80


# plot posterior probability distribution (on the above contrasts)
## HC inc prob 100 - 50
plotPost(HC_diff_inc_100_80, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## MDD inc prob 100 - 50
plotPost(MDD_diff_inc_100_80, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

## difference of the difference
plotPost(group_difference_inc_100_80, xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)

```

## Compute mean value for each condition from raw data

```{r}

ABN.raw.mean = group_by(ABN, group, accuracy, prob)

ABN.raw.mean = summarise(ABN.raw.mean, 
                         cond.mean = mean(power)) 
```

## Plot raw data

```{r, fig.height = 5, fig.width = 7}

# define label to set order of contidions to plot

ABN$label = paste0(ABN$group, ABN$accuracy, ABN$prob)

ABN$label = factor(ABN$label,
                   levels = c("HCcor100", "HCcor80", "HCcor50", "MDDT1cor100", "MDDT1cor80", "MDDT1cor50", 
                              "HCinc100", "HCinc80", "HCinc50", "MDDT1inc100", "MDDT1inc80", "MDDT1inc50"),
                   labels = c("HCcor100", "HCcor80", "HCcor50", "MDDcor100", "MDDcor80", "MDDcor50", 
                              "HCinc100", "HCinc80", "HCinc50", "MDDinc100", "MDDinc80", "MDDinc50"))

# different kinds of plots 

ABN %>%
  ggplot(aes(x = label, y = power)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
  stat_summary(fun.y=mean, geom="point", shape=1, size=5, color="black") +
  #geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
  theme(axis.text = element_text(size = 7),
        axis.title = element_text(size = 16))

ABN %>%
  ggplot(aes(x = label, y = power)) +
  stat_summary(fun.y=mean, geom="point", shape=4, size=10, color="black") +
  theme(axis.text = element_text(size = 7),
        axis.title = element_text(size = 16))

# boxplot + mean + 95% CI (bootstrap)

ABN %>%
  ggplot(aes(x = label, y = power, fill=group)) +
  geom_boxplot() +
  scale_fill_grey(start=0.8, end=0.5, labels = c("HC", "MDD")) + 
  theme_classic() +
  scale_x_discrete(breaks=c("HCcor100", "HCcor80", "HCcor50", "MDDcor100", "MDDcor80", "MDDcor50", 
                              "HCinc100", "HCinc80", "HCinc50", "MDDinc100", "MDDinc80", "MDDinc50"),
                  labels=c("cor\n100", "cor\n80", "cor\n50","cor\n100", "cor\n80", "cor\n50",
                           "inc\n100", "inc\n80", "inc\n50","inc\n100", "inc\n80", "inc\n50")) +     # labels for resp
                  # labels=c("pos\n100", "pos\n80", "pos\n50","pos\n100", "pos\n80", "pos\n50",
                  #          "neg\n100", "neg\n80", "neg\n50","neg\n100", "neg\n80", "neg\n50")) +     # labels for FB
  stat_summary(fun.y=mean, 
               geom="point", 
               shape=23, 
               size=3, 
               color="black", 
               fill="white") +
  stat_summary(fun.data = mean_cl_boot,
               geom = "errorbar",
               width = 0.3,
               size = 1,
               color = "white") +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14)) +
  labs(title="Response\n", x = "", y = "Power (dB)")                                # "\n" change for FB or resp





```



### Evaluate some hypothesis


# Model 4: main effects (accuracy,probability,group) and interaction prob : group
# 1) Posterior probability that FMT is lower in MDD vs HC (main effect of group)
# 2) Posterior probability that the prob effect is weaker for MDD vs HC (for 80 and 50)

```{r}
# Evid.Ratio is the ratio of P(groupMDDT1 < 0) / P(groupMDDT1 >= 0)
(hyp1 <- hypothesis(fit_full, "groupMDDT1 < 0"))
plot(hyp1)

# Evid.Ratio is the ratio of P(prob:groupMDDT1 < 0) / P(prob:groupMDDT1 >= 0)
(hyp2 <- hypothesis(fit_full, "prob80:groupMDDT1 < 0"))
plot(hyp2)

(hyp3 <- hypothesis(fit_full, "prob50:groupMDDT1 < 0"))
plot(hyp3)

```



### Playing around


# Model 4: main effects (accuracy,probability,group) and interaction prob : group

# --> main effect of MDD from averaging the post dist of each condition

# --> it's wrong. This mixes effect of group with effect of other predictor and interactions

```{r}

postHCavg = HCcor100 + HCcor80 + HCcor50 + HCinc100 + HCinc80 + HCinc50
postMDDavg = MDDcor100 + MDDcor80 + MDDcor50 + MDDinc100 + MDDinc80 + MDDinc50
  
plotPost((postHCavg - postMDDavg), xlab = "", col = "#b3cde0", showCurve = FALSE, cex = 1, compVal = 0)
  


```
### concluding: Information criteria does not evidence a overwhelming model. The model with main effects of acc and prob is performing comparably to the one with acc, prob and group, or the one with the 3 main effect and the interaction of prob with gtoup. Nevertheless, if we consider the latter model, there is strong evidence in favour of a lower FMT in the 50 and 80 prob conditions in MDD vs HC

# We might also maybe model the data with prob as continuous, and test the different slope of FMT across prob levels in the two groups